Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets

### 2018-08-10 doc/paper.Rmd
new style file added to account for author, old style file kept for now
Fixed heading bold-italic issues

\tableofcontents
\newpage
```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE,
  cache=TRUE
)
options(knitr.table.format = "latex")
library(tidyverse)
library(kableExtra)
library(xtable)
library(gridExtra)
```

@@

# Introduction

Same-source analyses are a major part of a Forensic Toolmark Examiner's job. In current practice, examiners  make these comparisons by visual inspection under a comparison microscope and come to one of the following four conclusions: identification, inconclusive, elimination or unsuitable for examination \cite{afte-toolmarks1998}. These conclusions are made on the basis of "unique surface contours" of the two toolmarks being in "sufficient agreement" \cite{afte-toolmarks1998}. AFTE describes the term "sufficient agreement" as the possibility of another tool producing the markings under comparison, as practically impossible \cite{afte-toolmarks1998}. Potential subject bias in the assessment as well as the lack of specified error rates are the main points of criticisms  first raised by the National Research Council in 2009 \cite{NAS:2009} and later emphasized further by the President's Council of Advisors on Science and Technology \cite{pcast2016}.

@@

# Methods

## Scans for land engraved areas

@@

## The Chumbley Score Test

@@

## A problem with failed tests

@@

## A modified approach

@@

## Testing setup

### The Data

@@

### Setup
Both algorithms (CS1) and (CS2) are implemented in R \citep{R}. (CS1) is available from package `toolmaRk` \citep{toolmark}, (CS2) is available from a modified version of the `toolmaRk` package available from GitHub (\url{https://github.com/heike/toolmaRk}). We applied both methods to all pairwise land-to-land comparisons of the Hamby scans provided by NIST for a total of 85,491 land-to-land comparisons.

# Results
## Failed Tests

@@

## Coarseness
The purpose of the coarseness parameter is to remove (sub-)class characteristics from profiles before comparisons for matching.
\citet{hadler} suggest a coarseness parameter of 0.25 in the setting of toolmark comparisons. For bullet lands, coarseness might need to be adjusted because of the strong effect  bullet curvature has on profiles.

@@

## Error rate assessment

@@

## Observed versus Nominal Type I error rates

@@

## High resolution Hamby 44 scans

@@

# Conclusions

@@

# Appendix
\begin{appendix}

>>>>

<!-- \tableofcontents -->
\newpage
```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE,
  cache=TRUE
)
options(knitr.table.format = "latex")
library(tidyverse)
library(kableExtra)
library(xtable)
library(gridExtra)
```

@@

<!-- # Introduction -->

<!-- \citeauthor{manytoolmarks2} -->
<!-- \citet{manytoolmarks2} -->
Same-source analyses are a major part of a Forensic Toolmark Examiner's job. In current practice, examiners  make these comparisons by visual inspection under a comparison microscope and come to one of the following four conclusions: identification, inconclusive, elimination or unsuitable for examination \cite{afte-toolmarks1998}. These conclusions are made on the basis of "unique surface contours" of the two toolmarks being in "sufficient agreement" \cite{afte-toolmarks1998}. AFTE describes the term "sufficient agreement" as the possibility of another tool producing the markings under comparison, as practically impossible \cite{afte-toolmarks1998}. Potential subject bias in the assessment as well as the lack of specified error rates are the main points of criticisms  first raised by the National Research Council in 2009 \cite{NAS:2009} and later emphasized further by the President's Council of Advisors on Science and Technology \cite{pcast2016}.

@@

# Methods {-}

## *Scans for land engraved areas* {-}

@@

## *The Chumbley Score Test* {-}

@@

## *A problem with failed tests* {-}

@@

## *A modified approach* {-}

@@

## *Testing setup* {-}

### The Data {-}

@@

### Setup {-}
Both algorithms (CS1) and (CS2) are implemented in R \citep{R}. (CS1) is available from package `toolmaRk` \citep{toolmark}, (CS2) is available from a modified version of the `toolmaRk` package available from GitHub (\url{https://github.com/heike/toolmaRk}). We applied both methods to all pairwise land-to-land comparisons of the Hamby scans provided by NIST for a total of 85,491 land-to-land comparisons.

# Results {-}
## *Failed Tests* {-}

@@

## *Coarseness* {-}
The purpose of the coarseness parameter is to remove (sub-)class characteristics from profiles before comparisons for matching.
\citet{hadler} suggest a coarseness parameter of 0.25 in the setting of toolmark comparisons. For bullet lands, coarseness might need to be adjusted because of the strong effect  bullet curvature has on profiles.

@@

## *Error rate assessment* {-}

@@

## *Observed versus Nominal Type I error rates* {-}

@@

## *High resolution Hamby 44 scans* {-}

@@

# Conclusions {-}

@@

# Appendix {-}
\begin{appendix}
